Supplementary material for: \nA comparison of single-cell trajectory inference methods

### 2018-11-12 manuscript/supplementary.Rmd
update paper & supplementary

# Supplementary figures
```{r, results="asis"}
sfigs %>% 
  left_join(refs %>% select(ref_id, name), "ref_id") %>% 
  arrange(name) %>% 
  select(-name) %>% 
  pmap(dynbenchmark:::plot_fig, ref_type = "sfig") %>% modify(paste0, "\n\n") %>% walk(cat)
```

@@

```{r, results="asis"}
stables %>% pmap(dynbenchmark:::show_table, ref_type = "stable") %>% modify(paste0, "\n\n") %>% walk(cat)
```

>>>>

# Supplementary figures
```{r, results="asis"}
sfigs %>% 
  left_join(refs %>% select(ref_id, name), "ref_id") %>% 
  arrange(name) %>% 
  select(-name) %>% 
  pmap(dynbenchmark:::plot_fig) %>% modify(paste0, "\n\n") %>% walk(cat)
```

@@

```{r, results="asis"}
stables %>% 
  left_join(refs %>% select(ref_id, name), "ref_id") %>% 
  arrange(name) %>% 
  select(-name) %>% 
  pmap(dynbenchmark:::show_table) %>% modify(paste0, "\n\n") %>% walk(cat)
```
